DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-29 paper/evaluation.tex
Change Pi3 specs in evaluation setup
Changed the size of the L1I cache.
Update evaluation section
Added the new figures and discussion regarding their findings.

The Raspberry Pi 3 Model B platform used in DeepPicar equips a Boardcom
BCM2837 SoC, which has a quad-core ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has a 16K private Instruction cache
and a 32K private Data cache, and all cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV
GPU, although we did not use the GPU in our evaluation due to the lack
of sofware support (TensorFlow is not compatible with the Raspberry Pi's GPU).
For software, we use Ubuntu MATE 16.04, TensorFlow 1.1 and Python
2.7. We disabled DVFS (dynamic voltage frequency scaling) and
configured the clock speed of each core statically at the maximum 1.2GHz.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore}
  \caption{Average control loop execution time vs. \#of CPU
    cores with cache partitioning enabled.}
  \label{fig:palloc_multicore}
\end{figure}

@@

@@

We run the DNN model with different amounts of L2 cache being
available based on the number of colors being used. For example, if two 
colors are used, then 25\% of the L2 cache is available, whereas if all 
8 colors are used, 100\% of the L2 cache is available. Particularly, we 
test the performance of the model when it utilizes a single core and
all four of the available cores. The results can be seen in 
\ref{fig:palloc_multicore}. As expected, the amount of L2 cache 
available to the model does not result in any significant changes in 
performance. As such, we find that a single model is not sensitive to 
the shared L2 cache.

@@

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in 
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater.

%TODO: Talk about the prefetcher, or something, for why the benchmark performance is worse.

>>>>

The Raspberry Pi 3 Model B platform used in DeepPicar equips a Boardcom
BCM2837 SoC, which has a quad-core ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has a 32K private Instruction cache
and a 32K private Data cache, and all cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV
GPU, although we did not use the GPU in our evaluation due to the lack
of sofware support (TensorFlow is not compatible with the Raspberry Pi's GPU).
For software, we use Ubuntu MATE 16.04, TensorFlow 1.1 and Python
2.7. We disabled DVFS (dynamic voltage frequency scaling) and
configured the clock speed of each core statically at the maximum 1.2GHz.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore}
  \caption{Average control loop execution time vs. \# % of L2 cache
  space available.}
  \label{fig:palloc_multicore}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore_l2missrate}
  \caption{L2 miss rate impact of limiting the amount of L2 cache space
  available to the DNN.}
  \label{fig:palloc_multicore_l2missrate}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_bus}
  \caption{Bus access impact of co-scheduling memory intensive co-runners 
when cache partitioning is enabled.}
  \label{fig:palloc_bandwidth_bus}
\end{figure}

@@

We run the DNN model with different amounts of L2 cache being
available based on the number of colors being used. For example, if two 
colors are used, then 25\% of the L2 cache is available, whereas if all 
8 colors are used, 100\% of the L2 cache is available. Particularly, we 
test the performance of the model when it utilizes a single core and
all four of the available cores. The results can be seen in 
\ref{fig:palloc_multicore}. As expected, the amount of L2 cache 
available to the model does not result in any significant changes in 
performance. This can also be seen by the L2 miss rates of the model 
seen in \ref{fig:palloc_multicore_l2missrate}. As more cache space 
becomes avaiable, the percentage of L2 misses decreases, which doesn't 
affect the real-time performance of the DNN. As such, we find that a 
single model is not sensitive to the shared L2 cache.

@@

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in 
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater.
At the same time, though, the L2 miss rates of the model don't correlate 
to the timing increases seen, as is shown in 
\ref{fig:palloc_bandwidth_l2missrate}. Instead, we find that the number
of bus accesses increases when cache partitions was used, and they mirror
the timing increases of the model. These additional bus accesses are
most likely caused by the L2 prefetcher, as it can generate additional bus
accesses that aren't counted as L2 misses. As a result, we find that cache
partitioning is detrimental to the performance of the DNN so long as the 
L2 prefetcher is enabled (we have not yet found a way to disable it on
the Pi 3). Furthermore, no cache sensitivity was displayed by the model,
thus showing that the performance of the L2 cache is not vital for DNN 
performance when co-runners are introduced.
